\textsc{HubbleCLIP}: Learning associations between astronomical data and natural language with multi-modal models

### 2023-11-21 paper/main.tex

\documentclass[10pt]{article} % For LaTeX2e
\usepackage{tmlr}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{tmlr}
% To de-anonymize and remove mentions to TMLR (for example for posting to preprint servers), instead use the following:
%\usepackage[preprint]{tmlr}

@@

\usepackage{hyperref}
\usepackage{url}

\title{Learning associations between astronomical data and natural language with multi-modal models}

@@

\author{\name Kyunghyun Cho \email kyunghyun.cho@nyu.edu \\
      \addr Department of Computer Science\\
      University of New York
      \AND
      \name Raia Hadsell \email raia@google.com \\
      \addr DeepMind
      \AND
      \name Hugo Larochelle \email hugolarochelle@google.com\\
      \addr Mila, Universit\'e de Montr\'eal \\
      Google Research\\
      CIFAR Fellow}

% The \author macro works with any number of authors. Use \AND 
% to separate the names and addresses of multiple authors.

@@

\section{Introduction}

>>>>

\documentclass[10pt]{article} % For LaTeX2e
\usepackage[preprint]{tmlr}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{tmlr}
% To de-anonymize and remove mentions to TMLR (for example for posting to preprint servers), instead use the following:
%\usepackage[preprint]{tmlr}

@@

\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}

\title{\textsc{HubbleCLIP}: Learning associations between astronomical data and natural language with multi-modal models}

@@

\author{\name Siddharth Mishra-Sharma \email smsharma@mit.edu \\
      \addr The NSF AI Institute for Artificial Intelligence and Fundamental Interactions\\
      Center for Theoretical Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA \\
      Department of Physics, Harvard University, Cambridge, MA 02138, USA
      \AND
      \name Yiding Song \email ydsong@mit.edu \\
      \addr The NSF AI Institute for Artificial Intelligence and Fundamental Interactions\\
      Department of Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA \\
      \AND
      \name Jesse Thaler \email jthaler@mit.edu \\
      \addr The NSF AI Institute for Artificial Intelligence and Fundamental Interactions\\
      Center for Theoretical Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA \\
}
% The \author macro works with any number of authors. Use \AND 
% to separate the names and addresses of multiple authors.

@@

\section{Introduction}
\label{sec:intro}

\section{Dataset and Processing}
\label{sec:dataset}

\section{Methodology}
\label{sec:methodology}

\subsection{Language-Image Pre-training}
\label{sec:pretraining}

\subsection{Pre-trained CLIP Model}
\label{sec:clip}

\subsection{Fine-tuning Objectives}
\label{sec:finetuning}

\section{Results and Discussion}
\label{sec:results}

\subsection{Fine-tuned Retrieval Accuracy}
\label{sec:retrieval_acc}

\subsection{`Zero-shot' Hypothesis and Object Retrieval}
\label{sec:zero_shot}

\subsection{Text-to-Image Retrieval}
\label{sec:tti}

\cite{Hinton06}

\begin{figure*}[!h]
\includegraphics[width=0.95\textwidth]{plots/retrieval_acc.pdf}
\caption{Retrieval accuracy}
\label{fig:retrieval_acc}
\end{figure*}

\begin{figure*}[!h]
\includegraphics[width=0.95\textwidth]{plots/itt.pdf}
\caption{Retrieval accuracy}
\label{fig:itt}
\end{figure*}

\begin{figure*}[!h]
\includegraphics[width=0.95\textwidth]{plots/tti_base.pdf}
\caption{Retrieval accuracy}
\label{fig:tti}
\end{figure*}

\begin{figure*}[!h]
\includegraphics[width=0.95\textwidth]{plots/tti.pdf}
\caption{Retrieval accuracy}
\label{fig:tti_base}
\end{figure*}
